---
title: "Justin Gregoire's CV"
date: "`r Sys.Date()`"
params: 
  your_name: 
    value: "Justin Gregoire"
  pdf_export: 
    value: TRUE
  sheet_ss_id: 
    value: "1SqkIDpyVfurLA0DXRgcsZ9aba_Bk9bvak0sGRCLsVX0"
  online_link:
    value: "https://jtgregoire93.github.io/resume"
  pdf_location: 
    value: "https://github.com/jtgregoire93/resume/raw/main/resume.pdf"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css','css/styles.css','resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)
library(googlesheets4)
library(crayon)
library(googledrive)
library(gluedown)
library(fontawesome)
library(tippy)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- params$pdf_export
your_name <- params$your_name
# ss id of your google sheet, using mine here

# Holds all the links that were inserted for placement at the end

source('parsing_functions.R') # Functions for building sections from CSV data
source('common_variables.R')  # Small variables for non-csv data such as intro text

# Refactored code
position_data <- read_sheet(params$sheet_ss_id, sheet = "entries", skip = 1) %>% 
  filter(in_resume) %>% 
  mutate(
    section = case_when(
      section %in% c('industry_positions') ~ 'positions', 
      TRUE ~ section
    )
  ) 

intro_text <- read_sheet(params$sheet_ss_id, sheet = "text_blocks", skip = 1) %>%
  select("text") %>% 
  as.character()

skills <- read_sheet(params$sheet_ss_id, sheet = "skills", skip = 1) 

contact_info <-
  read_sheet(params$sheet_ss_id, sheet = "contact_info", skip = 1)
location <-
  contact_info %>% filter(loc == 'location')  %>% select(entry, link) 
email <-
  contact_info %>% filter(loc == 'email')  %>% select(entry, link)  
phone <-
  contact_info %>% filter(loc == 'phone')  %>% select(entry, link)  
linkedin <-
  contact_info %>% filter(loc == 'linkedin')  %>% select(entry, link)  
github <-
  contact_info %>% filter(loc == 'github')  %>% select(entry, link)  
calendly <-
  contact_info %>% filter(loc == 'calendly')  %>% select(entry, link) 

location <- contact_info %>% 
            filter(loc == 'location')  %>% 
            select(entry, link) 

email <- contact_info %>% 
         filter(loc == 'email')

```

# Aside

### Contact {#contact}

-   [![](map-pin.svg){style="color:red" width="8%"}](https://goo.gl/maps/Kq3da8KnpZdFY6nd7) `r location %>% select(entry)`
-   [![](envelope.svg){width="8%"}](mailto:jtgregoire93@gmail.com) `r email %>% select(entry) %>% as.character()`
-   [![](phone.svg){width="8%"}](tel:+1757-619-7431) `r phone %>% select(entry)`
-   Socials: [![](linkedin.svg){width="8%"}](https://www.linkedin.com/in/justin-gregoire) [![](github.svg){width="8%"}](https://github.com/jtgregoire93). [![](calendar-days.svg){width="8%"}](https://calendly.com/jtgregoire93/30-minute-call)

### Education {data-icon="graduation-cap" data-concise="true"}

-   **`r position_data %>% filter(section == 'education') %>% select("institution")`**
-   `r position_data %>% filter(section == 'education') %>% select("title")`
-   `r paste0(position_data %>% filter(section == 'education') %>% select("start"), '-', position_data %>% filter(section == 'education') %>% select("end"))`

### **Technical Skills**

-   `r skills %>% filter(loc == 'technical') %>% select("skill1")`

-   `r skills %>% filter(loc == 'technical') %>% select("skill2")`

-   `r skills %>% filter(loc == 'technical') %>% select("skill3")`

### **Strategic Skills**

-   `r skills %>% filter(loc == 'strategic') %>% select("skill1")`

-   `r skills %>% filter(loc == 'strategic') %>% select("skill2")`

-   `r skills %>% filter(loc == 'strategic') %>% select("skill3")`

### **Toolset**

-   `r skills %>% filter(loc == 'toolset') %>% select("skill1")`

-   `r skills %>% filter(loc == 'toolset') %>% select("skill2")`

-   `r skills %>% filter(loc == 'toolset') %>% select("skill3")`

#### Access {#files}

```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("[Online version](", params$online_link, ")")
} else {
  cat("[<i class='fas fa-download'></i> Download PDF version](", params$pdf_location, ")")
}
```

# Main

## `r your_name` {#title}

```{r message=FALSE, warning=FALSE}
cat(paste0(intro_text, sep = "\n"))
```

## Professional Experience {data-icon="suitcase"}

```{r comment=NA, results='asis'}
position_data %>% print_section('positions') 
```
